---
title: "Final Group Project: AirBnB Analytics"
date: "16/10/2021"
author: "Group-A15 - Vincent Lyu, Johnna Liu, Michael Hiski, Dhruv Ghurburrun, Helena Martin, Dhruv Pathak"
output:
  html_document:
    highlight: zenburn
    theme: flatly
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: show
---


```{r setup, include=FALSE}
# leave this chunk alone
options(knitr.table.format = "html") 
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
  comment = NA, dpi = 300)
```


```{r load-libraries, echo=FALSE}

library(tidyverse) # the usual stuff: dplyr, readr, and other goodies
library(lubridate) # to handle dates
library(GGally) # for correlation-scatter plot matrix
library(ggfortify) # to produce residual diagnostic plots
library(rsample) # to split dataframe in training- & testing sets
library(janitor) # clean_names()
library(broom) # use broom:augment() to get tidy table with regression output, residuals, etc
library(huxtable) # to get summary table of all models produced
library(kableExtra) # for formatting tables
library(moderndive) # for getting regression tables
library(skimr) # for skim
library(mosaic)
library(leaflet) # for interactive HTML maps
library(tidytext)
library(viridis)
library(vroom)
```


```{r load_data, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

# use cache=TRUE so you dont donwload the data everytime you knit

listings <- vroom("http://data.insideairbnb.com/belgium/bru/brussels/2021-09-24/data/listings.csv.gz") %>% 
       clean_names()

```


# Executive Summary 

> Simply put, what we have done here is taken a rough data set, cleaned it, and run some analysis to communicate some interesting observations and predictions regarding AirBnB's presence in Brussels. We started by converting variables to formats that would be of use to us. Then, we selected certain variables from the raw data set on the basis of their usefulness in conducting regressions, data visualisations, correlation tests, etc. Using these variables, we plotted bar charts, distribution charts, and more. Lastly, we ran regressions and made some predictions. 

## Data Visualisation 

> We approached the data visualisation with the objective of challenging pre-concieved notions we had regarding relationships between a cusomter and seller in the AirBnB context. Through some qualitative analysis, we answered questions such as "What is the relationship between the quality of a host (seller) and the price they charge" and compared results to our hypotheses. 

## Regression Analysis

### Creating the explained variable

> For the regression part, we started by creating a new variable called **Price_4_nights** to calculate the cost of staying 4 nights at an Airbnb. Given we were looking specifically at the cost for 2 people, we filtered the data to calculate the cost for only Airbnb’s which could accommodate at least 2 people. However, for the regression model, we have instead decided to create and use **log_Price_4_nights** as the explained variable since its distribution is close to a normal distribution. Before, starting with the different regression models, we split total dataset into trained and tested the data set.

#### Models Results

> **Model 1**     
For Model 1, we have tested the significance of **property type**, the **number of reviews** and **review score rating** on the price of an airBnB. At first glance, there is a negative relationship between review score rating and the price for 4 nights at an Airbnb, which seems strange given that normally we would expect properties having higher ratings will have higher prices. However, the negative relationship is very small and is nearly zero and it is not statistically significant. Other variables are significant.`Prop_type_simplified` is a categorical variable, so the first thing we should understand is this regression is choosing `entire condo` as a base line. The intercept can be interpreted as an entire condominium (condo) will command a log price_4_nights of 5.883. If another property type is chosen such as a private room in rental unit or a private room in residential home, then the log price will be decreased by 0.563 and 0.430 respectively. This make sense as the price of renting a room will be lower than that of an entire condo. In general, property type is a significant predictor of price of an AirBnb. Checking for collinearity, we can see that this is not an issue here in this model due to VIF being lower than 5.  Then we run model 1 on our tested dataset, and RMSE = 0.518    
**Model 2**      
In model 2, we find `review_score_rating` is insignificant, so we drop it in our following regression. For model 2, we want to determine if room type is a significant predictor of the cost for 4 nights and we find out that every room type, except for a hotel room, is a significant predictor of price. Again, checking for collinearity, we can see that this is not an issue here in this model due to VIF being lower than 5. Checking for overfitting, we find the RMSE = 0.504 on tested data set.       
**Model 3**          
For model 3, we want to determine if number of *bathrooms*, *bedrooms*, *bed* and *size of the house* are significant predictors of the cost for 4 nights. The number of beds is not significant predictors of `log_price_4_nights`. However, the number of bedrooms, bathrooms and size of the house are significant predictors. Given VIF is less than 5, it doesn't seem that there is any issue of multi-collinearity. Checking for overfitting, we find the RMSE = 0.441 on tested data set.      
**Model 4**   
For model 4, we want to understand if superhosts (`host_is_superhost`) command a pricing premium, after controlling for other variables.  At first glance, being a superhost seems command a pricing premium compared to being not. However, it is not statistically significant. So we have 95% confidence to say being a superhost doesn't command a pricing premium. Given VIF is less than 5, it doesn't seem that there is any issue of multi-collinearity. We find the RMSE = 0.418 on tested data set.   
**Model 5**  
`host_is_superhost` is not significant, so we don’t include it in our regression. For model 5, we want to see if the fact that some hosts allows you to immediately book their listing may command a price premium compared to those who don’t. We find out that being able to instantly book an Airbnb is a significant predictor of price. Given VIF is less than 5, it doesn't seem that there is any issue of multi-collinearity. Checking RMSE on tested data set, we find RMSE = 0.441.  
**Model 6**    
For model 6, we have created a new variable called `neightbourhood_simplified`, where we broke down the 19 neighbourhoods in Brussels into 5 neighbourhood based on where they are located in the city of Brussels. We separed the different neighbourhoods into neighbourhoods located in the North West, North East, East/Centre, West/Centre and South/Centre.  Location is a good significant predictor of `log_price_4_nights` as seen by t-statistics. Rooms located in the East won't have a significant effect on price, however, rooms located in North East, North West, South have significant postive effect on `price_4_night`. Again, given VIF is less than 5, it doesn't seem that there is any issue of multi-collinearity. Checking RMSE on tested data set, we find RMSE = 0.441.       
**Model 7**       
For model 7, we try to find the effect of the variable `avalability_30` or `reviews_per_month` on `log_price_4_nights`, after we control for other variables. For this model, we find `number_of_reviews` is not significant, then we try to replace it with `review_scores_rating`, then this is significant. This might because `reviews_per_month` could represent much information of `number_of_review`, so this variable become insignificant. We also find that `availability_30` and `reviews_per_month` have significant positive effect on `price_4_nights`. Again, given VIF is less than 5, it doesn't seem that there is any issue of multi-collinearity. Checking RMSE on tested data set, we find RMSE = 0.3703.

##### Prediction

>**Choosing a model**   
Model 7 has the highest adjusted R^2, and also the lowest RMSE in testing set, which means model7 has the best explaining ability with no overfitting. So we use model7 for prediction.\
**Prediction**  
Suppose I want to order a private room in rental unit, located in North West. We want this room to have more than 10 reviews with an average score rating higher than 4.5. Based on the existing dataset, our point estimation for the price I should pay for 4 nights is 123.4 Euros, and 95% upper price is 131.6 Euros, 95% lower price is 115.7 Euros.


# Exploratory Data Analysis (EDA)


## Data wrangling


```{r, data_lookey}
glimpse(listings)
skim(listings, where(is.numeric))
skim(listings, where(is.factor))
skim(listings, where(is.Date))
skim(listings, where(is.logical))
```

### Step 1: Glimpse and Skim Results 

#### How many variables/columns? How many rows/observations?

>There are 74 variables and 5442 rows

#### Which variables are numbers?

> ***There are 37 numeric variables. They are:***  
- id  
- scrape_id  
- host_id  
- host_listings_count  
- host_total_listings_count  
- latitude  
- longitude  
- accommodates  
- bedrooms  
- beds  
- minimum_nights  
- maximum_nights  
- minimum_minimum_nights  
- maximum_minimum_nights  
- minimum_maximum_nights  
- maximum_maximum_nights  
- minimum_nights_avg_ntm  
- maximum_nights_avg_ntm  
- availability_30  
- availability_60  
- availability_90  
- availability_365  
- number_of_reviews  
- number_of_reviews_ltm  
- number_of_reviews_130d   
- review_scores_rating   
- review_scores_accuracy  
- review_scores_cleanliness  
- review_scores_checkin  
- review_scores_communication  
- review_scores_location  
- review_scores_value  
- calculated_host_listings_count  
- calculated_host_listings_count_entire_homes  
- calculated_host_listings_count_private_rooms  
- calculated_host_listings_count_shared_rooms  
- reviews_per_month

#### Which are categorical or *factor* variables (numeric or character variables with variables that have a fixed and known set of possible values?

> ***Categorical vriables:***   
- host_verifications  
- host_has_profile_pic  
- host_identity_verified  
- neighbourhood  
- neighbourhood_cleansed  
- property_type   
- room_type  
- has_availability  
- instant_bookable
  

```{r data_cleaney}
listings <- listings %>% 
  mutate(price = parse_number(price),
         bathrooms = parse_number(bathrooms_text))
typeof(listings$price)
typeof(listings$bathrooms)
```
  
### Step 2: Computing summary statistics of the variables of interest, or finding NAs

```{r variables_of_interest_new_listings}
# select some important varialbes to calculate summary statistics
important_var <- c('host_listings_count', 'host_total_listings_count', 'accommodates', 'bathrooms','bedrooms', 'beds', 'price', 'minimum_nights', 'maximum_nights', 'minimum_minimum_nights', 'maximum_minimum_nights', 'minimum_maximum_nights', 'minimum_nights_avg_ntm', 'maximum_nights_avg_ntm', 'availability_30', 'availability_60', 'availability_90', 'availability_365', 'number_of_reviews', 'number_of_reviews_ltm', 'number_of_reviews_l30d', 'review_scores_rating', 'review_scores_accuracy')

listings[, c(important_var)] %>% 
  pivot_longer(cols = c(1:23), names_to = 'variable', values_to = 'value' ) %>% 
  group_by(variable) %>% 
  summarise(favstats(value))

#Variables of interests
new_listings <- listings %>% 
  select(host_since, host_location, host_response_time, host_response_rate, host_is_superhost, host_neighbourhood, host_listings_count, host_total_listings_count, host_has_profile_pic, host_identity_verified, neighbourhood_cleansed, latitude, longitude, property_type, room_type, accommodates, bathrooms, bedrooms, beds, price, minimum_nights, maximum_nights, minimum_nights_avg_ntm, maximum_nights_avg_ntm, has_availability, number_of_reviews, review_scores_rating, instant_bookable, availability_30,  reviews_per_month)

skim(new_listings, where(is.numeric))
skim(new_listings, where(is.factor))
skim(new_listings, where(is.Date))
skim(new_listings, where(is.logical))

```

#### Skim Summary of variables of interest

> Based on the results of skim, there are 229 missing values in description, 2230 missing in neighborhood_overview, 2 missing in host_name, 16 missing in host_location, 2656 missing in host_about, 2 missing in host_response time, host_response_rate, host_acceptance_rate, host_thumbnail_rul, host_picture_url, 2028 missing in host_neighbourhood, 2230 missing in neighbourhood, 12 missing in bathrooms_text, 2 missing in host_since, 914 missing in first_review and last_review, 2 missing in host_is_superhost, host_has_profile_pic, host_identity_verified, 5442 missing in neighbourhood_group_cleansed, bathrooms, calendar_updated and license.
Furthermore, there are 16 missing in host_location,  2 missing in host_response time, host_response_rate, host_acceptance_rate, 2028 missing in host_neighbourhood,2 missing in host_since,2 missing in host_is_superhost, host_has_profile_pic, host_identity_verified. 


## Propery types


````{r pivoting_new_listings}
new_listings %>% 
  count(property_type) %>% 
  arrange(desc(`n`)) %>% 
  pivot_wider(names_from = property_type, values_from = n) %>% 
  mutate(total = rowSums(.)) %>% 
  pivot_longer(col = 1:45, names_to = 'property_type', values_to = 'count' ) %>% 
  mutate(proportion = count / total)

```

#### What are the top 4 most common property types? What proportion of the total listings do they make up? 

> The top 4 property type are 'Entire rental unit', 'Private room in rental unit', 'Entire condominium (condo)', and 'Private room in residential home', their proportions are 52.7%, 13.2%, 5.48%, 5.20%.

```{r new_listings_mutuate1}
new_listings <- new_listings %>%
  
 mutate(prop_type_simplified = case_when(
    property_type %in% c("Entire rental unit","Private room in rental unit", "Entire condominium (condo)","Private room in residential home") ~ property_type, 
    TRUE ~ "Other"
  ))

```


```{r new_listings_cleaning_illus2}
new_listings %>%
  count(property_type, prop_type_simplified) %>%
  arrange(desc(n))        
```              
    

```{r new_listings_cleaning_illus3}
new_listings %>% 
  mutate(minimum_nights = as.factor(minimum_nights)) %>% 
  group_by(minimum_nights) %>% 
  count() %>% 
  arrange(desc(n))
```

#### What are the  most common values for the variable `minimum_nights`? 

> The most common value is 1 day. 

#### Is there any value among the common values that stands out? 

> 90, 30 days stand out among those common values

#### What is the likely intended purpose for Airbnb listings with this seemingly unusual value for `minimum_nights`?

> The unusual values are either 1 month or 1 quater, which indicates that house hosts have high intention to let their house for long-term purpose (1 month or 1 quater)


```{r}
new_listings <- new_listings %>% 
  filter(minimum_nights <= 4) #filtering data to only allow have a min of 4 nights
```
        
# Mapping 

```{r, out.width = '80%'}

leaflet(data = filter(listings, minimum_nights <= 4)) %>% 
  addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addCircleMarkers(lng = ~longitude, 
                   lat = ~latitude, 
                   radius = 1, 
                   fillColor = "blue", 
                   fillOpacity = 0.4, 
                   popup = ~listing_url,
                   label = ~property_type)
```


## Visualizations 

> What we intend to do in the next section is use the visualisation tools we have learnt so far to answer some interesting questions we have come up with it.


### What type of room is most common in Brussels (In terms of Number of Rooms) and on average how many people do these room types accomodate? 

```{r viz_1, fig.width= 12}
# Creating the data table that we will use to plot the top room frequency graph
top_room_type <- new_listings %>% 
  group_by(room_type) %>% 
  summarise(room_type_count = count(room_type))

# Creating the data table that we will use to plot the top average accommodating room type graph
average_number_accomodated_by_room_type <- new_listings %>% 
  group_by(room_type) %>% 
  summarise(average_accomodated = mean(accommodates))


room_type_bar_graph <- top_room_type %>% 
  ggplot(aes(x = room_type_count, y = fct_reorder(room_type, room_type_count))) +
  geom_col(fill='yellow') +
  theme_bw()+
  labs(
    title = "What type of listings (by room type) are most common in Brussels?",
    subtitle = NULL,
    x = "Count",
    y = NULL )

room_type_bar_graph

average_number_accomodated_bar_graph <- average_number_accomodated_by_room_type %>% 
   ggplot(aes(x = average_accomodated, y = fct_reorder(room_type, average_accomodated))) +
   geom_col(fill='blue') +
   theme_bw()+
   labs(
    title = "On average, which type of room accomodates the most people?",
    subtitle = NULL,
    x = "Average Number Accomodated",
    y = NULL )

average_number_accomodated_bar_graph
```

#### Comments and Analysis

> The objective of this first question was to determine the nature of AirBnB listings (by type of rooms) and, as a result, understand the nature of house ownership in Brussels. Furthermore, these graphs can help us conjecture, qualitatively, whether the capcity (in terms of numbers accomodated) has any bearing on the frequency of the type of AirBnB listings.\
Firstly, we would hypothesize that, to an extent, the higher the number accomodated by a type of a room, the more their frequency as an AirBnB listing. The results suggest that this is partially true, namely that Entire apartments are the most common and the ones that accomodate the most. This makes sense as the larger room-types are what can be charged slightly more for. We do see that this relationship doesn't hold for hotel rooms. This also makes sense as Hotel Rooms are generally not listed on AirBnB but their own websites. 
        
### What is the AirBnB Price distribution in Brussels? 

```{r viz_2, fig.width= 12}
price_by_prop_type_histo <- ggplot(new_listings, aes(x = price))+ 
  geom_boxplot(outlier.colour = "red", outlier.shape =8, outlier.size =4) +
  facet_wrap(~room_type)+
  theme_bw()+
  xlim(0,300)+
  labs(title = "AirBnB listings in Brussels' price distribution",
         x = "Price", 
         y = "")
price_by_prop_type_histo 

price_by_prop_type_density <- ggplot(new_listings, aes(x = price))+ 
  geom_density(fill = 'orange')+
  theme_bw()+
  xlim(0,300)+
  facet_wrap(~ room_type)+
  labs(title = "AirBnB listings in Brussels' price distribution",
         x = "Price", 
         y = "", )
price_by_prop_type_density

```

#### Comments and Analysis

> The objective here was to identify how the price of listings are distributed with the listings grouped by room-type. What we note here is that all the distributions are right skewed and (pretty much) multi-modal. The implicaiton here of this result is that the mean price is greater than the median. Speciically, there are certain listings that are priced significantly above the typical price, resultantly skewing the distribution. This is a result we can expect, particullarly in the context of luxury listings. 

### How is the price of the listing related to how long a host has been a host for? 

```{r viz_3, fig.width= 12}
# Creation of column that states how long a host has been a host by days
new_listings <- new_listings %>% 
  mutate(todays_date = Sys.Date())
new_listings <- new_listings %>% 
  mutate(days_since_host = difftime(todays_date ,host_since , units = c("days")))

ggplot(new_listings, aes(x = days_since_host , y= price))+ 
  geom_point(colour = 'turquoise') +
  theme_bw()+
  labs(title = "Relationship between price and how long an inidividual has been a host",
         x = "Host Tenure", 
         y = "Price")+
   scale_y_log10()
```

#### Comments and Analysis

> The objective here is to understand whether there is a relationship between how long a host has been a host and the price they charge for their listings.\
We hypothesized that there is a positive relationship between the two due to the notion that a host with a longer tenure is likley to be more reputable and thus has the power to charge more. Qualitatively, according to the graph above, this relationship is not obvious. If we think this through, we can conclude that is very much likely that host tenure has absolutely nothing to do with how much the host charges. Instead, other factors such as location, type of room, host ratings, etc. are likely to have a bigger bearing on whether a host charges more or less. 
   
### How is Host quality, measured by whether a Host is a Super Host or not, correlated with Price? 
           
```{r viz_4, fig.width= 12}
# Converting a logical into binary variable
cols <- sapply(new_listings, is.logical)
new_listings[,cols] <- lapply(new_listings[,cols], as.numeric)

ggplot(new_listings, aes(x = host_is_superhost , y= price))+ 
  geom_point(colour = 'red') +
  theme_bw()+
  labs(title = "Relationship between a host being a superhost and the price they charge",
         x = "Superhost? (1 = Yes, 0 = No)", 
         y = "Price")

dummy_model_quality <- lm(price ~ host_is_superhost, data = new_listings)
summary_dummy <- summary(dummy_model_quality)
print(summary_dummy)
```
 
#### Comments and Analysis 

> Besides charting a scatter-plot and trying to conjecture on the relationship between the x and y variable, the objective of this question was to convert a logical categorical variable into a binary regressor and then interpret the results of a linear model. The interpretation of the results are not that of a typical linear regression that we can interpret as usual.\ 
The hypothesis here was that, on average, superhosts charge more for listings than non-superhosts. Instead, we get the statistically significant result at the 95% level that, on average, superhosts charge $13.34 less than non-superhosts. This is an interesting result. We need to realise that of course, there are liklely to be various confounding variables and that what we have here is far from causality. But, based solely on this bivariate model, we can come up with the following story as to why we see this relationship: The reason why a certain host is a superhost is because they don't overcharge. 
 
### Analysing multiple correlations with the help of GGpairs
 
> In the following analysis, we use the GGpairs plot to qualitatively answer a set of questions based on relationships between two variables. 


```{r viz_5, fig.width= 12}
# GGpairs plot to answer it all
new_listings %>% 
  select(price, minimum_nights, maximum_nights, beds, host_identity_verified, review_scores_rating) %>% 
  ggpairs(aes(alpha=0.1))+
  theme_bw()
```

#### What is the relationship between the minimum number of nights you can book a listing and the listings price? 
 
> We would conjecture that as the number of minimum nights increases, the listing price would decrease and this is in fact the case (correlations, not causation). The negative correlation of -0.043, albeit weak, makes sense as setting a higher minimum number nights is a restriction for customers that has to compensated for with lower prices by the host. 
 
#### What is the relationship between the number of beds and listing's price? 

> We would expect that the correlation between number of beds and price to be positive. The results describe a weak positive correlation of 0.252. The logic behind this is relatively obvious. Bigger beds would imply a bigger house/unit. The customer would be expected to pay for a bigger house. The reason why the correlation isn't strong, howerver, could be because of the confounding factors we have not factored in such as location, for example. 

#### What is the relationship between whether a host is verified and the listing's price?

> We could expect that if a host is verified, they have more credibility and thus can charge a higher price. Oddly, there is a very weak negative correlation of -0.009. Again, there are numerous confounders that would stop us from making conclusive statements. Perhaps adding other regressors would return a positive correlation. 


# Regression Analysis

```{r}
#Creation of variable price_4_nights
new_listings <- new_listings %>%
  filter(accommodates > 1) %>%
  mutate(price_4_nights = price * 4)
```

```{r}
#creating new variables called `neighbourhood_simplified` for later regression

new_listings <- new_listings %>%
  mutate(neighbourhood_simplified = case_when(neighbourhood_cleansed %in% c("Jette","Berchem-Sainte-Agathe","Koekelberg", "Molenbeek-Saint-Jean", 
                                       "Ganshoren") ~ "North West", 
                                       neighbourhood_cleansed %in% c( "Saint-Josse-ten-Noode", "Schaerbeek",  "Bruxelles", "Evere") ~ "North East", 
                                      neighbourhood_cleansed %in% c("Woluwe-Saint-Lambert", "Woluwe-Saint-Pierre","Auderghem", "Etterbeek") ~ "East/Centre",
                                      neighbourhood_cleansed %in% c("Saint-Gilles", "Anderlecht", "Forest") ~ " West/Centre",
                                      neighbourhood_cleansed %in% c("Ixelles", "Uccle", "Watermael-Boitsfort") ~ "South/Centre"))

```


```{r price for y}
#Creation of new variable log-Price_4_nights
new_listings <- new_listings %>%
  mutate(log_price_4_nights = log(price_4_nights))

#Creating a histogram to examine distribution of price_4_nights
ggplot(data = new_listings, aes(x = price_4_nights)) +
  geom_histogram(color = "white", fill = "steelblue") +
  theme_bw() +
  labs(title = "Distribution of price_4_nights in histogram graph",
         x = "price_4_nights", 
         y = "")

```

```{r, log price for y}

#Creating a histogram to examine distribution of log(price_4_nights)
ggplot(data = new_listings, aes(x = log_price_4_nights)) +
  geom_histogram(color = "white", fill = "steelblue") +
  theme_bw() +
  labs(title = "Distribution of log(price_4_nights) in histogram graph",
         x = "log(price_4_nights)", 
         y = "")
```

#### Which variable should you use for the regression model? Why?

> We should use log(price_4_nights) for the model as its distribution is a normal distribution. 

## Set training and testing dataset

```{r}
library(rsample)
set.seed(1234)

#new_listings <- new_listings %>% na.omit()  #drop na
train_test_split <- initial_split(new_listings, prop = 0.7)
train_data <- training(train_test_split)
test_data <- testing(train_test_split)
```


## Model 1

```{r}
#checking the types of prop_type-simplified
new_listings %>%
  group_by(prop_type_simplified) %>%
  summarise(n = n()) %>% 
  arrange(desc(n))
```
```{r}
# Fit regression model
model1 <-lm(log(price_4_nights) ~ prop_type_simplified + number_of_reviews + review_scores_rating, data = train_data)

msummary(model1)

```
```{r, fig.width = 9, fig.height= 9 }
autoplot(model1)
```

#### Interpreting the coefficient `review_scores_rating` in terms of `price_4_nights`.

> At first glance, there is a negative relationship between review_scores_ratings and price_4_nights, which seems strange given that normally we would expect properties having higher ratings will have higher prices. However, the negative relationship is very small and is nearly zero and it is not statistically significant. So we have 95% confidence to see review_scores_rating does not have too much effect on price_4_nights. 

#### Interpreting the coefficient of `prop_type_simplified` in terms of `price_4_nights`.

> prop_type_simplified is a categorical variable, so the first thing we should understand is this regression is choosing `entire condo` as a base line. The intercept can be interpreted as an entire condominium (condo) will command a log price_4_nights of 5.883. If another property type is chosen such as a private room in rental unit or a private room in residential home, then the log price will be decreased by 0.563 and 0.430 respectively. This make sense as the price of renting a room will be lower than that of an entire condo. 

### Checking for Overfitting

```{r}
# testing overfit
RMSE_model1 <- test_data %>% 
  mutate(predictions = predict(model1, .),
         R = predictions - log_price_4_nights) %>%#. automatically fund data we need 
  select(R) %>% 
  na.omit() %>%  # omit all the NA values in residual
  summarise(RMSE = sqrt(sum(R**2 / n()))) %>% 
  pull()
RMSE_model1
  
```


## Model 2

We want to determine if `room_type` is a significant predictor of the cost for 4 nights, given everything else in the model. Fit a regression model called model2 that includes all of the explananatory variables in `model1` plus `room_type`. 

> Since `review_score_rating` is not a significant variable, we don't put it in our regression model

```{r}

# Fit regression model
model2 <-lm (log_price_4_nights ~ prop_type_simplified + number_of_reviews + room_type, data = train_data)

msummary(model2)

```

> Except for `room_typeHotel room`, other Room type is a significant predictor of price as see by t-statistics. 

### Checking for Overfitting

```{r}
# testing overfit
RMSE_model2 <- test_data %>% 
  mutate(predictions = predict(model2, .),
         R = predictions - log_price_4_nights) %>%#. automatically fund data we need 
  select(R) %>% 
  na.omit() %>%  # omit all the NA values in residual
  summarise(RMSE = sqrt(sum(R**2 / n()))) %>% 
  pull()
RMSE_model2
  
```
```{r, fig.width=9, fig.height=9}
autoplot(model2)
```

## Extending our Analysis: Our Models

## Model 3


```{r}
# Fit regression model
model3 <-lm (log(price_4_nights) ~ prop_type_simplified + number_of_reviews + room_type + bathrooms + bedrooms + beds + accommodates  , data = train_data)

msummary(model3)

```

### Checking for Colinearity

```{r}
car::vif(model3)
```

#### Are the number of `bathrooms`, `bedrooms`, `beds`, or size of the house (`accomodates`) significant predictors of `price_4_nights`? Or might these be co-linear variables?

> The number of beds is not significant predictors of price_4_nights. However, the numberof bedrooms, bathrooms and size of the house are significant predictors. Given VIF is less than 5, it doesn't seem that there is any issue of multi-collinearity. 

### Checking for Overfitting

```{r}
# testing overfit
RMSE_model3 <- test_data %>% 
  mutate(predictions = predict(model3, .),
         R = predictions - log_price_4_nights) %>%#. automatically fund data we need 
  select(R) %>% 
  na.omit() %>%  # omit all the NA values in residual
  summarise(RMSE = sqrt(sum(R**2 / n()))) %>% 
  pull()
RMSE_model3
  
```
```{r, fig.width=9, fig.height=9}
autoplot(model3)
```

## Model 4

#### Do superhosts `(host_is_superhost`) command a pricing premium, after controlling for other variables?

> Since `beds` is not a significant variable, we discard it

```{r}
# Fit regression model
model4 <-lm (log_price_4_nights ~ prop_type_simplified +review_scores_rating+ number_of_reviews + room_type + bathrooms + bedrooms + accommodates + host_is_superhost  , data = train_data)

msummary(model4)
```

### Checking for Colinearity

```{r}
car::vif(model4)
```

### Checking for Overfitting

```{r}
# testing overfit
RMSE_model4 <- test_data %>% 
  mutate(predictions = predict(model4, .),
         R = predictions - log_price_4_nights) %>%#. automatically fund data we need 
  select(R) %>% 
  na.omit() %>%  # omit all the NA values in residual
  summarise(RMSE = sqrt(sum(R**2 / n()))) %>% 
  pull()
RMSE_model4
  
```

#### Key Comments 

> At first glance, being a superhost seems command a pricing premium compared to being not. However, it is not statistically significant. So we have 95% confidence to say being a superhost doesn't command a pricing premium.

```{r, fig.width=9, fig.height=9}
autoplot(model4)
```


## Model 5


```{r}
# Fit regression model
model5 <-lm (log(price_4_nights) ~ prop_type_simplified + number_of_reviews  + room_type + bathrooms + bedrooms + 
               accommodates +  instant_bookable , data = train_data)

msummary(model5)
```

### Checking for Colinearity

```{r}
car::vif(model5)
```

### Checking for Overfitting

```{r}
# testing overfit
RMSE_model5 <- test_data %>% 
  mutate(predictions = predict(model5, .),
         R = predictions - log_price_4_nights) %>%#. automatically fund data we need 
  select(R) %>% 
  na.omit() %>%  # omit all the NA values in residual
  summarise(RMSE = sqrt(sum(R**2 / n()))) %>% 
  pull()
RMSE_model5
  
```
```{r, fig.width=9, fig.height=9}
autoplot(model5)
```

#### After controlling for other variables, is `instant_bookable` a significant predictor of `price_4_nights`?

> Instant_bookable is a significant predictor of price as seen by t statistics. 

####  Use your city knowledge, or ask someone with city knowledge, and see whether you can group neighbourhoods together so the majority of listings falls in fewer (5-6 max) geographical areas. 

> We have a member of our study group from Brussels. He suggests we group neighbourhoods into 'North West', 'North East', 'East', 'West', 'South'

```{r}
new_listings <- new_listings %>%
  mutate(neighbourhood_simplified = case_when(neighbourhood_cleansed %in% c("Jette","Berchem-Sainte-Agathe","Koekelberg", "Molenbeek-Saint-Jean", 
                                       "Ganshoren") ~ "North West", 
                                       neighbourhood_cleansed %in% c( "Saint-Josse-ten-Noode", "Schaerbeek",  "Bruxelles", "Evere") ~ "North East", 
                                      neighbourhood_cleansed %in% c("Woluwe-Saint-Lambert", "Woluwe-Saint-Pierre","Auderghem", "Etterbeek") ~ "East/Centre",
                                      neighbourhood_cleansed %in% c("Saint-Gilles", "Anderlecht", "Forest") ~ " West/Centre",
                                      neighbourhood_cleansed %in% c("Ixelles", "Uccle", "Watermael-Boitsfort") ~ "South/Centre"))


```

## Model 6

```{r}
# Fit regression model
model6 <-lm (log_price_4_nights ~ prop_type_simplified + number_of_reviews  + room_type + bathrooms + bedrooms  + 
               accommodates + instant_bookable + neighbourhood_simplified , data = train_data)

msummary(model6)
```

### Checking for Colinearity

```{r}
car::vif(model6)
```

### Checking for Overfitting

```{r}
# testing overfit
RMSE_model6 <- test_data %>% 
  mutate(predictions = predict(model5, .),
         R = predictions - log_price_4_nights) %>%#. automatically fund data we need 
  select(R) %>% 
  na.omit() %>%  # omit all the NA values in residual
  summarise(RMSE = sqrt(sum(R**2 / n()))) %>% 
  pull()
RMSE_model6
  
```
```{r, fig.width=9, fig.height=9}
autoplot(model6)
```

#### Key Comments 

> Location is a good significant predictor of `price_4_nights` as seen by t-statistics. Rooms located in the East won't have a significant effect on price, however, rooms located in North East, North West, South have significant postive effect on `price_4_night`

1. What is the effect of `avalability_30` or `reviews_per_month` on `price_4_nights`, after we control for other variables?

## Model 7

```{r}
# Fit regression model
model7 <-lm (log_price_4_nights ~ prop_type_simplified +  number_of_reviews + room_type + bathrooms + bedrooms +  
               accommodates +  instant_bookable + neighbourhood_simplified + reviews_per_month + availability_30 , data = train_data)

# Get regression table:
msummary(model7)
                    
```

#### Key Comments 

> For this model, we find number_of_reviews is not significant, then we try to replace it with review_scores_rating, then this is significant. This might because reviews_per_month could represent much information of number_of_review, so this variable become insignificant.

```{r}
# Fit regression model
model7 <-lm (log_price_4_nights ~ prop_type_simplified + review_scores_rating + room_type + bathrooms + bedrooms +  
               accommodates +  instant_bookable + neighbourhood_simplified + reviews_per_month + availability_30 , data = train_data)

# Get regression table:
msummary(model7)
                    
```


### Checking for Colinearity

```{r}
car::vif(model7)
```


### Checking for Overfitting


```{r}
# testing overfit
RMSE_model7 <- test_data %>% 
  mutate(predictions = predict(model7, .),
         R = predictions - log_price_4_nights) %>%#. automatically fund data we need 
  select(R) %>% 
  na.omit() %>%  # omit all the NA values in residual
  summarise(RMSE = sqrt(sum(R**2 / n()))) %>% 
  pull()
RMSE_model7
  
```
```{r, fig.width=9, fig.height=9}
autoplot(model7)
```

#### Key Comment 

> `availability_30` and `reviews_per_month` have significant positive effect on `price_4_nights`

## Creating summary tables

```{r}
#library(huxtable)
huxreg(list('model1' = model1,
            'model2' = model2, 
            'model3' = model3, 
            'model4' = model4, 
            'model5' = model5, 
            'model6' = model6, 
            'model7' = model7),
       
       statistics = c('#observations' = 'nobs', 
                      'R squared' = 'r.squared', 
                      'Adj. R Squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
                 bold_signif = 0.05, 
                 stars = NULL
) %>% 
  set_caption('Comparison of models')
```

#### Note

> RMSE in the testing dataset

```{r}
data_frame(RMSE_model1,RMSE_model2,RMSE_model3,RMSE_model4, RMSE_model5,
          RMSE_model6,RMSE_model7)
```

#### Note

> Model 7 has the highest adjusted R^2, and also the lowest RMSE in testing set, which means model7 has the best explaining ability with no overfitting. So we use model7 for prediction.


## Prediction using our model of choice


```{r}
data <- new_listings %>% 
  filter(review_scores_rating >= 4.5,
         prop_type_simplified == 'Private room in rental unit',
         room_type == 'Private room',
         number_of_reviews >= 10,
         neighbourhood_simplified == 'North West') 

data %>% 
  mutate(predictions = predict(model7,.)) %>% 
  select(predictions) %>% 
  summarise(mean = mean(predictions, na.rm = TRUE), 
            std = sd(predictions, na.rm =TRUE),
            count = n(),
            SE = std / sqrt(count),
  # get t-critical value with (n-1) degrees of freedom,
            t = qt(0.975, count - 1),
            margin_of_error = t * SE,
            lower_CI = mean - margin_of_error,
            higher_CI = mean + margin_of_error) %>% 
  select(mean, std, lower_CI, higher_CI) %>% 
  mutate(mean = exp(mean),
         lower_CI = exp(lower_CI),
         higher_CI = exp(higher_CI))
```


### Our Answer to the prediction 

> Suppose I want to order a private room in rental unit, located in North West. We want this room to have more than 10 reviews with an average score rating higher than 4.5. Based on the existing dataset, our point estimation for the price I should pay for 4 nights is 123.4 Euros, and 95% upper price is 131.6 Euros, 95% lower price is 115.7 Euros.
